Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-01-30 WSSSPE1_report/WSSSPE1_summary_report.tex
fix latex error
Updates to the development/support section
Began fleshing out what subsections/points might be made, with help
from the papers and shared Google document.

@@

@@

\subsection{What are communities?}
\subsection{Challenges of community}
include metrics for community success (e.g., more external contributors than internal).
\subsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\subsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities)
\item courses on online communities
\item books
\item need for software carpentry module on organizing communities?
\end{itemize}

>>>>

\subsection{Research or Reuse?}

Discussion of software produced as a by-product versus software developed for reuse. How does this change the project, who develops the code, growth beyond 1--2 person projects to larger projects with diverse set of consumers and contributors. Modular and extensible code versus working for current research problem---tackled by same people, or a collaborative team?

\subsection{Defining Sustainability for Scientific Software}

What is sustainable? What are the best practices, can workshops fund meetings to help define and improve best practices in these areas? Software plans from the funding agencies?

\subsection{Training Scientists to Develop and Support Software}

Discussion of the evolving role of scientists, and/or others that fill these roles.

\subsection{Software Process, Code Review, Automation, Reproducibility}

There are a lot of tools out there, but few are currently used. Look at what some projects have found successful, and how to automate as much as possible to reduce additional overhead.

\subsection{Software and Data Licensing}

Its impact on how and where research products are used, who can collaborate and what patterns have worked/not worked in existing communities.

\subsection{Funding, Sustainability Beyond the First Grant/Institution}

How initial software development is funded, moving to follow up projects, maintenance, community growth, collaborating with other institutions, labs, industry, internationally. Contract relationship versus collaborative development between scientists and software developers.

\subsection{Training Others to use Software}

Who creates training materials, how are they distributed, integration into courses when projects see very wide application in research.

@@

\subsection{Career Tracks for Scientific Software Developers}

How to ensure software is sustainable by ensuring there are career paths for developers.

@@

\subsection{What are communities?}
\subsection{Challenges of community}
include metrics for community success (e.g., more external contributors than internal).
\subsection{Admirable scientific software communities}
\begin{itemize}
\item example communities
\item their (quick) origin stories.
\end{itemize}
\subsection{Resources for learning about software communities}
\begin{itemize}
\item academic fields studying communities (and software communities)
\item courses on online communities
\item books
\item need for software carpentry module on organizing communities?
\end{itemize}
